Nice people or potential cooperators when keeping promises

### 2019-08-09 behavioral-promises/behavioral-promises.tex
Author correction
authors

\author{  Said Jiménez \and  Kamila E. Sip \and  Roberto E. Mercadillo \and  Diego Angeles-Valdez \and  Jairo Muñoz-Delgado \and  Juan J. Sánchez-Sosa \and  Eduardo A. Garza-Villarreal \and  }

@@

\institute{
        Said Jiménez \at
     Department of Psychology, National University of México (UNAM) \\
     \email{\href{mailto:said.ejp@gmail.com}{\nolinkurl{said.ejp@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Kamila E. Sip \at
     Institute for Neuroleadership \\
     \email{\href{mailto:kami.sip@gmail.com}{\nolinkurl{kami.sip@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Roberto E. Mercadillo \at
     Department of Biology, Universidad Autónoma Metropolitana (UAM) \\
     \email{\href{mailto:emmanuele.mercadillo@gmail.com}{\nolinkurl{emmanuele.mercadillo@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Diego Angeles-Valdez \at
     Institute of Neurobiology, UNAM \\
     \email{\href{mailto:anglsd_20@hotmail.com}{\nolinkurl{anglsd\_20@hotmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Jairo Muñoz-Delgado \at
     Investigaciones en Neurociencias, INPRF \\
     \email{\href{mailto:munozd460@gmail.com}{\nolinkurl{munozd460@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Juan J. Sánchez-Sosa \at
     Department of Psychology, National University of México (UNAM) \\
     \email{\href{mailto:jujosaso@gmail.com}{\nolinkurl{jujosaso@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Eduardo A. Garza-Villarreal \at
     Institute of Neurobiology, UNAM \\
     \email{\href{mailto:egarza@gmail.com}{\nolinkurl{egarza@gmail.com}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

>>>>

\author{  Said Jiménez  \and  Roberto E. Mercadillo \and  Diego Angeles-Valdez \and  Jairo Muñoz-Delgado \and  Juan J. Sánchez-Sosa \and  Eduardo A. Garza-Villarreal \and  }

@@

\institute{
        Said Jiménez \at
     Department of Psychology, National University of México (UNAM) \\
     \email{\href{mailto:said.ejp@gmail.com}{\nolinkurl{said.ejp@gmail.com}}}  %  \\
 %           \emph{Present address:} of F. Author  %  if needed
    }
